---
title: "Project 2 DATA2002"
date: "`r Sys.Date()`"
author: "550770402"
format: 
  html: 
    embed-resources: true # Creates a single HTML file as output
    code-fold: true # Code folding; allows you to show/hide code chunks
    code-tools: true # Includes a menu to download the code file
    theme: lux
    # code-tools are particularly important if you use inline R to 
    # improve the reproducibility of your report
execute: 
  warning: false
  message: false
  echo: True
table-of-contents: true # (Optional) Creates a table of contents
number-sections: true # (Optional) Puts numbers next to heading/subheadings
---

## Abstract

## Introduction

## Dataset

```{r}
# IMPORTS
library(ggplot2)
```

| Variable | Type   | Description                      |
|----------|--------|----------------------------------|
| 1        | Input  | Fixed acidity                    |
| 2        | Input  | Volatile acidity                 |
| 3        | Input  | Citric acid                      |
| 4        | Input  | Residual sugar                   |
| 5        | Input  | Chlorides                        |
| 6        | Input  | Free sulfur dioxide              |
| 7        | Input  | Total sulfur dioxide             |
| 8        | Input  | Density                          |
| 9        | Input  | pH                               |
| 10       | Input  | Sulphates                        |
| 11       | Input  | Alcohol                          |
| 12       | Output | Quality (score between 0 and 10) |

Missing Attribute Values: None <https://archive.ics.uci.edu/dataset/186/wine+quality>

```{r}
# RED WINE 
RED <- read.csv2("winequality-red.csv")

# Red wine quality graph 
ggplot(RED, aes(x = factor(quality))) +
  geom_bar() +
  labs(
    title = "Red Wine Quality",
    x = "Quality score",
    y = "Number of wines"
  ) +
  theme_minimal()
```

```{r}
# WHITE WINE 
WHITE <- read.csv2("winequality-white.csv")

# White wine quality graph 
ggplot(WHITE, aes(x = factor(quality))) +
  geom_bar() +
  labs(
    title = "White Wine Quality",
    x = "Quality score",
    y = "Number of wines"
  ) +
  theme_minimal()

```

```{r}
# Dataset sizes
cat("Red wine:", nrow(RED), "rows x", ncol(RED), "columns\n")
cat("White wine:", nrow(WHITE), "rows x", ncol(WHITE), "columns\n")
```

## Analysis

### Model Selection

When developing the model to use, I first had to determine the independence of attributes of the wine. This involved grouping some parameters into categories to assess their potential relation, those being:

- Acidity (Fixed Acidity, Volatile acidity, Citric acid)\
  Fixed acidity are a set of acids in wine which do not evaporate at normal temperatures, and are often contrasted with Volatile acids, which are a wine's gaseous acids. These are mutually exclusive options for acids, and therefore it is valuable to include both in a linear model.

- Sulphates (Free sulfur dioxide, Total sulfur dioxide)\
  dvbhjdf\
  efsbjkdfv\
  dvfklnjdf

- Fermentation (Residual sugar, Alcohol) \
  svdjdfv\
  svdjkvd\
  dvjkndfjk

### Model Evaluation

### Assumptions

## Findings

## Conclusions

## Acknowledgements

<https://winefolly.com/deep-dive/what-is-residual-sugar-in-wine/>

<https://winefolly.com/deep-dive/sulfites-in-wine/>

<https://www.laithwaites.com.au/blog/wine-knowledge/what-are-sulphites-in-wine?srsltid=AU7gw4V7stof4SfbOUvMWdx4ULW-JOi90X2Y10K2BZ43BTuilEW5OkNQ>

<https://www.extension.iastate.edu/wine/total-sulfur-dioxide-why-it-matters-too>

<https://extension.okstate.edu/fact-sheets/understanding-free-sulfur-dioxide-fso2-in-wine>

<https://allen.in/science/citric-acid>

<https://www.wineenthusiast.com/basics/drinks-terms-defined/volatile-acidity-wine/?srsltid=AU7gw4WLNjSRE_L8EV5xUtPLNiQOfeHsq6PGgl7BJQRdxK4-F4NxreI2>

<https://familiamorgan.com/learn/glossary/fixed-acidity/?srsltid=AU7gw4UXMx3POoBA8MtxK5lc3ZS53_a0dGRl4YQsJJi2-3TC6bBni4q4>

P. Cortez, A. Cerdeira, F. Almeida, T. Matos and J. Reis. Modeling wine preferences by data mining from physicochemical properties. In Decision Support Systems, Elsevier, 47(4):547-553. ISSN: 0167-9236.
